Global patterns of forest autotrophic carbon fluxes

### 2021-02-25 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

ForC contains geographic coordinates associated with each measurement record and, when available, $MAT$ and $MAP$ as reported in the primary literature [@anderson-teixeira_forc_2018]. Based on the geographic co-ordinates for each site, data on twelve climate variables -- including $MAT$, $MAP$, temperature seasonality (*i.e.*, standard deviation across months), precipitation seasonality (*i.e.*, coefficient of variation of mean monthly precipitation), annual temperature range, solar radiation, cloud cover, annual frost and wet days, potential evapotranspiration ($PET$), aridity ($MAP/PET$), and vapor pressure deficit ($VPD$) -- were extracted from five open-access climate datasets: WorldClim [@hijmans_very_2005], WorldClim2 [@fick_worldclim_2017], the Climate Research Unit time-series dataset (CRU TS v4.03 [@harris_updated_2014], the Global Aridity Index and Potential Evapotranspiration Climate Database [@trabucco_global_2019], and TerraClimate [@abatzoglou_terraclimate_2018] (Table S1). Definitions and methods used to calculate each variable are included in Table S1. From these data, we derived maximum $VPD$, defined as the $VPD$ of the month with the largest deficit, and the number of water stress months, defined as the number of months annually where precipitation was lower than $PET$. Where site-level data was missing for $MAT$ or $MAP$, we used values from the WorldClim dataset.

>>>>

ForC contains geographic coordinates associated with each measurement record and, when available, $MAT$ and $MAP$ as reported in the primary literature [@anderson-teixeira_forc_2018]. Based on the geographic co-ordinates for each site, data on twelve climate variables -- including $MAT$, $MAP$, temperature seasonality (*i.e.*, standard deviation across months), precipitation seasonality (*i.e.*, coefficient of variation of mean monthly precipitation), annual temperature range, solar radiation, cloud cover, annual frost and wet days, potential evapotranspiration ($PET$), aridity ($MAP/PET$), and vapor pressure deficit ($VPD$) -- were extracted from five open-access climate datasets: WorldClim [@hijmans_very_2005], WorldClim2 [@fick_worldclim_2017], the Climate Research Unit time-series dataset (CRU TS v4.03) [@harris_updated_2014], the Global Aridity Index and Potential Evapotranspiration Climate Database [@trabucco_global_2019], and TerraClimate [@abatzoglou_terraclimate_2018] (Table S1). Definitions and methods used to calculate each variable are included in Table S1. From these data, we derived maximum $VPD$, defined as the $VPD$ of the month with the largest deficit, and the number of water stress months, defined as the number of months annually where precipitation was lower than $PET$. Where site-level data was missing for $MAT$ or $MAP$, we used values from the WorldClim dataset.
